```{r}
setwd("C:/Users/vaibhav/Desktop/datasciencecoursera")
data<-read.csv("hw1_data.csv")
View(data)
```
In the dataset provided for this Quiz, what are the column names of the dataset?
```{r}
head(data)
```
Extract the first 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
data[1:2,]
```
How many observations (i.e. rows) are in this data frame
```{r}
nrow(data)
```
Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
data[152:153,]
```
What is the value of Ozone in the 47th row?
```{r}
data[47,1]
```
How many missing values are in the Ozone column of this data frame?
```{r}
no_of_Na<-is.na(data$Ozone)
table(no_of_Na)
```
What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
newdata<-subset(data,!no_of_Na)
mean(newdata$Ozone)
```
Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
newdata1<-subset(data,data$Ozone>31 & data$Temp>90)
mean(newdata1$Solar.R)
```
What is the mean of "Temp" when "Month" is equal to 6?
```{r}
newdata2<-subset(data,data$Month==6)
mean(newdata2$Temp)
```

What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
newdata3<-subset(data,data$Month==5 & !is.na(data$Ozone))
max(newdata3$Ozone)
```

